The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
102

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 101~stars too bright to have been otherwise observed. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of \textcolor{red}{101} targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

>>>>

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise observed. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.
